### 2014-03-14 src/paper.Rnw
update

\begin{comment}
<<setup, include=FALSE, message=FALSE, echo=FALSE>>=
is.installed <- function(mypkg) is.element(mypkg, installed.packages()[,1])
options(CRAN = "http://cran.stat.ucla.edu")
if (!is.installed("xtable")) install.packages("xtable")
if (!is.installed("ggplot2")) install.packages("ggplot2")
if (!is.installed("reshape2")) install.packages("reshape2")

>>>>

\begin{comment}
<<setup, include=FALSE, message=FALSE, echo=FALSE>>=
is.installed <- function(mypkg) is.element(mypkg, installed.packages()[,1])
#options(CRAN = "http://cran.stat.ucla.edu")
#if (!is.installed("xtable")) install.packages("xtable")
#if (!is.installed("ggplot2")) install.packages("ggplot2")
#if (!is.installed("reshape2")) install.packages("reshape2")
